Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
edits to 3.5

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$,
e.g. did the agent correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Tbl.~\ref{baselineComparisons}
compares our model against these baselines.
Our full model consistently
beats the baselines,
and that the recognition model 
consistently increases the number of solved held-out tasks.
Lesioning the recognition model also slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Fig.~\ref{learningCurves}).
This supports our view of the recognition model as a way of accelerating the search over programs.

>>>>

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$,
e.g. did the agent correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Tbl.~\ref{baselineComparisons}
compares our model against these baselines.
Our full model consistently beats the baselines.
Lesioning the recognition model slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Fig.~\ref{learningCurves}).
This supports our view of the recognition model as a way of accelerating the search over programs.
